### 2013-10-18 manuscripts/reply/reply-main.tex
Moving sections of `reply.tex` into separate files.
Moving the main text, tables, and figures of `reply.tex` to
`reply-main.tex`, `reply-tables.tex`, and `reply-figures.tex`.

%&<latex>
\documentclass[letterpaper,12pt]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/macros.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\doublespacing
\raggedright
\setlength{\parindent}{0.5in}
\begin{linenumbers}

\begin{titlepage}
    \begin{flushleft}
        \sffamily

        \MakeUppercase{\large\bfseries Why you should not fix a biased
        model-choice method by adding an additional dimension of model choice:
        A reply to Hickerson et al.}

        \vspace{12pt}
        \textbf{Running head:} \MakeUppercase{Approximate Bayesian model
        choice}

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Jacob A.\
        Esselstyn$^{4}$, Charles W.\ Linkem$^{5}$, Cameron D.\
        Siler$^{6}$, Mark T.\ Holder$^{1}$ and Rafe M.\ Brown$^{1}$

        \bigskip
        $^1$\emph{Department of Ecology and Evolutionary Biology,
            Biodiversity Institute,
            University of Kansas,
            Lawrence, Kansas 66045}\\[.1in]
        $^3$\emph{Department of Biology,
            Duke University,
            Durham, North Carolina 27708} \\[.1in]
        $^4$\emph{Museum of Natural Science,
            Louisiana State University,
            119 Foster Hall,
            Baton Rouge, Louisiana 70803}\\[.1in]
        $^5$\emph{Department of Biology,
            University of Washington,
            Seattle, Washington 98195}\\[.1in]
        $^6$\emph{Sam Noble Museum,
            Department of Biology,
            University of Oklahoma,
            Norman, Oklahoma 73072}\\[.1in]
        $^2$\emph{Corresponding author} (\href{mailto:joaks1@gmail.com}{\tt
        joaks1@gmail.com})\\

    \end{flushleft}
\end{titlepage}

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    with low likeihood and high prior density that is imposed by broad uniform
    priors.
    \citet{Hickerson2013} have responded to this work, criticising the priors
    used by \citet{Oaks2012} and presenting an approximate Bayesian
    model-averaging approach that uses narrow, empirically informed uniform
    priors.
    \citet{Hickerson2013} use this method to re-analyze the empirical dataset
    of \citet{Oaks2012} comprised of 22 pairs of vertebrate populations from
    the Philippines, and conclude the model-averaging approach circumvents the
    issues revealed by \citet{Oaks2012} and yields robust inference of
    divergence models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of low marginal likelihoods of parameter-rich models.
    Here we discuss an error in the methodology of \citet{Hickerson2013} that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate that the approach of \citet{Hickerson2013} is
    biased toward models with less parameter space, which manifests in a strong
    tendency to sample predominantly from models that exclude the true values
    of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show the approach of \citet{Hickerson2013} is still biased toward
    inferring simultaneous divergences even when the true divergences are
    randomly distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    low marginal likelihoods of complex models is a primary cause of the bias
    of \msb toward models with less parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using questionable
    empirically informed uniform priors.

    \vspace{12pt}
    \noindent\textbf{KEY WORDS: Approximate Bayesian computation; Bayesian
        model choice; empirical Bayes}

}

\newpage

%CWL:
% \highLight{The goal of this paper needs to be to highlight the major
%     differences of opinion on how ABC can be used in comparative phylogeography
%     and how these changes to msbayes can be made that will improve the
%     inference in the future. We should avoid nit-picking the Hickerson paper
%     and try to stay positive.}

\noindent Recently, this journal has served as a medium for a
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses
showing that \msb can often be biased toward inferring models of temporally
clustered divergence times across taxon pairs.
\citet{Hickerson2013} published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially mitigate this issue.

@@

\section*{Acknowledgments}
We thank the National Science Foundation for supporting this work (DEB
1011423).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

\bibliography{../bib/references}
% \bibliography{references}

%% LIST OF FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

\renewcommand\listfigurename{Figure Captions}
\cftsetindents{fig}{0cm}{2.2cm}
\renewcommand\cftdotsep{\cftnodots}
\setlength\cftbeforefigskip{10pt}
\cftpagenumbersoff{fig}
\listoffigures

\end{linenumbers}

%% TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\singlespacing

%:TABLE-re-analysis
% \begin{table}[htbp]
%     \sffamily
%     \footnotesize
%     \addtolength{\tabcolsep}{-0.08cm}
%     \rowcolors{2}{}{myGray}
%     %\captionsetup{font=footnotesize}
%     \caption{Results of the model-averaging approach of \citet{Hickerson2013}
%         applied to the Philippines dataset of \citet{Oaks2012} using eight
%         prior models (see \citet{Hickerson2013} Table 1).  The results of (1)
%         \citet{Hickerson2013}, (2) our full re-analysis, and of (3) repeating
%         the final rejection step of \citet{Hickerson2013} using the prior means and
%         standard deviations to normalize the summary statistics, are all compared.}
%     \centering
%     \begin{tabular}{ l l l l }
%         \toprule
%          & Hickerson et al. (2013) & Re-analysis & blah \\
%         $\hat{\numt{}}$ & 2 & 1 & 1 \\
%         $p(\numt{} = 1 | \ssSpace)$ & 0.062 & 0.206 & 0.146 \\
%         $BF_{\numt{} = 1, \numt{} \neq 1}$ 1.39 & 5.45 & 3.59 \\
%         $p(\vmratio{} < 0.01 | \ssSpace)$ & 0.298 & 0.416 & 0.361 \\
%         $BF_{\vmratio{} < 0.01, \vmratio{} \geq 0.01}$ 6.65 & 11.16 & 8.85 \\
%         $\hat{M}$ & 1 & 2 & 2 \\
%         $p(M_1 | \ssSpace)$ & 0.513 & 0.358 & 0.376 \\
%         $p(M_2 | \ssSpace)$ & 0.286 & 0.369 & 0.389 \\
%         $p(M_3 | \ssSpace)$ & 0.036 & 0.086 & 0.089 \\
%         $p(M_4 | \ssSpace)$ & 0.002 & 0.012 & 0.011 \\
%         $p(M_5 | \ssSpace)$ & 0.142 & 0.129 & 0.107 \\
%         $p(M_6 | \ssSpace)$ & 0.020 & 0.043 & 0.024 \\
%         $p(M_7 | \ssSpace)$ & 0.001 & 0.003 & 0.004 \\
%         $p(M_8 | \ssSpace)$ & 0.000 & 0.000 & 0.001 \\
%         \bottomrule
%     \end{tabular}
%     \label{tabModelChoiceEmpirical}
% \end{table}

%:TABLE-model-choice-empirical
\begin{table}[htbp]
    \sffamily
    % \footnotesize
    \addtolength{\tabcolsep}{-0.08cm}
    \rowcolors{2}{}{myGray}
    %\captionsetup{font=footnotesize}
    \caption{Results of the model-averaging approach of \citet{Hickerson2013}
        applied to the Philippines dataset of \citet{Oaks2012} using three sets
        of prior models. All models used priors on population size of
        $\meanDescendantTheta{} \sim U(0.0001,0.1)$ and $\ancestralTheta{} \sim
        U(0.0001, 0.05)$, and differ only in their prior on divergence time
        (\divt{}) parameters.  Each set of five models differ only in the
        divergence time prior used for the model with the narrowest prior:
        $M_1$ ($\divt{} \sim U(0, 0.1)$), $M_{1A}$ ($\divt{} \sim U(0, 0.01)$),
        or $M_{1B}$ ($\divt{} \sim U(0, 0.001)$). The approximate posterior
        probability of each model ($p(M_i \given \ssSpace)$) is given for each
        of the three analyses.  The posterior estimates are based on 10,000
        samples retained from $1\e6$ prior samples
    from each model.}
    \centering
    \begin{tabular}{ l l l l l }
        \toprule
        & & \multicolumn{3}{c}{$p(M_i \given \ssSpace)$} \\
        \cmidrule(){3-5}
        Model & \divt{} prior & $M_{*}=M_1$ & $M_{*}=M_{1A}$ & $M_{*}=M_{1B}$ \\
        \midrule
        $M_*$ & --        & 0.899 & 0.821 & 0.673 \\
        $M_2$ & $U(0,1)$  & 0.079 & 0.136 & 0.251 \\
        $M_3$ & $U(0,5)$  & 0.013 & 0.026 & 0.044 \\
        $M_4$ & $U(0,10)$ & 0.006 & 0.012 & 0.022 \\
        $M_5$ & $U(0,20)$ & 0.003 & 0.005 & 0.010 \\
        \bottomrule
    \end{tabular}
    \label{tabModelChoiceEmpirical}
\end{table}

\clearpage

%% FIGURES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\mFigure{../../response-redux/hickerson-et-al-posterior/hickerson-posterior-1k/mean_by_dispersion.pdf}{
    The joint posterior of the mean (\meant{}{}) and dispersion index ($\vmratio{} = 
    \vart{}{}/\meant{}{}$) of divergence times for 22 vertebrate taxon pairs as
    estimated by \citet{Hickerson2013} (see Figure 2B of \citet{Hickerson2013}).
    The posterior samples are color-coded to indicate the erroneous mixture of
    timescales in the analysis of \citet{Hickerson2013};
    grey = $0.05/\mutationRate$ generations and
    black = $0.02/\mutationRate$ generations.
}{figJointPosteriorHickerson}

% \mFigure{../images/coin_flip.pdf}{
%     A plot of three beta probability density functions that represent a prior
%     (black; $beta(0.5, 0.5)$), true posterior (blue; $beta(4.5, 1.5)$), and
%     empirical Bayes density (red; $beta(8.5, 2.5)$) for a dataset of five
%     Bernoulli trials, four of which are successes.
% }{figCoinFlip}

\mFigure{../../model-choice/priors-for-pc-plot/pc-plots.pdf}{
    The graphical checks recommended by \citet{Hickerson2013} for three prior
    models: (A) $M_1$ ($\divt{} \sim U(0, 0.1)$), (B) $M_{1A}$ ($\divt{} \sim
    U(0, 0.01)$), and (C) $M_{1B}$ ($\divt{} \sim U(0, 0.001)$).
    The plots project the summary statistics from 1000 random samples from each
    model onto the first two orthogonal axes of a principle component analysis,
    with the blue dot representing the observed summary statistics from the 22
    population pairs of Philippine vertebrates.
}{figPCA}

%% Exclusion simulation results
\mFigure{../../model-choice/results/m1-1-sim/pymsbayes-results/num_tau_excluded.pdf}{
    The propensity of the model-averaging approach of \citet{Hickerson2013} to
    exclude the truth.
    The plots illustrate the number of true \divt{} parameters excluded from analyses of
    simulated datasets where \divt{} for 22 pairs of populations is drawn from an
    exponential distribution, $\divt{} \sim Exp(2)$.
    The plots represent (A) unadjusted and (B) GLM-adjusted estimates from 1000
    simulation replicates analyzed using $5\e6$ samples from the prior.
    The proportion of simulation replicates in which at least one true
    parameter value is excluded from the model preferred by a Bayes factor
    ($p(\divt{} \notin \hat{M})$) is also given.
}{figExclusionSimTau}

\mFigure{../../model-choice/results/m1-1-sim/pymsbayes-results/prob_of_exclusion.pdf}{
    The propensity of the model-averaging approach of \citet{Hickerson2013} to
    exclude the truth.
    The plots illustrate the estimated probability of excluding at least one
    true \divt{} value from analyses of simulated datasets where \divt{} for 22
    pairs of populations is drawn from an exponential distribution, $\divt{}
    \sim Exp(2)$.
    The plots represent (A) unadjusted and (B) GLM-adjusted estimates from 1000
    simulation replicates analyzed using $5\e6$ samples from the prior.
    The proportion of simulation replicates in which there is strong support
    for at least one true parameter value being excluded from the model
    ($p(BF_{\divt{} \notin M, \divt{} \in M} > 10)$) is also given.
}{figExclusionSimProb}

%% Power results
\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_accuracy_omega_median.pdf}{
    The accuracy of the model-averaging approach of \citet{Hickerson2013} to
    estimate the dispersion index of divergence times (\vmratio{}) from
    analyses of simulated datasets where \divt{} for 22 pairs of populations is
    drawn from a series of uniform distributions, $\divt{} \sim U(0,
    \divt{max})$.
    The proportion of estimates less than the true value of,
    $p(\hat{\vmratio{}} < \vmratio{})$, is given for each \divt{max}.
    Each plot represents unadjusted median estimates from 500 simulation
    replicates analyzed using $5\e6$ samples from the prior.
}{figPowerAccOmegaMedian}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_accuracy_omega_mode_glm.pdf}{
    The accuracy of the model-averaging approach of \citet{Hickerson2013} to
    estimate the dispersion index of divergence times (\vmratio{}) from
    analyses of simulated datasets where \divt{} for 22 pairs of populations is
    drawn from a series of uniform distributions, $\divt{} \sim U(0,
    \divt{max})$.
    The proportion of estimates less than the true value of,
    $p(\hat{\vmratio{}} < \vmratio{})$, is given for each \divt{max}.
    Each plot represents GLM-regression-adjusted mode estimates from 500
    simulation replicates analyzed using $5\e6$ samples from the prior.
}{figPowerAccOmegaModeGLM}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_psi_mode.pdf}{
    The bias of the model-averaging approach of \citet{Hickerson2013} to infer
    clustered divergences in our simulation-based power analyses.
    The plots illustrate the estimated number of divergence events ($\hat{\numt{}}$)
    from analyses of simulated datasets where \divt{} for 22 pairs of populations is drawn from a series of
    uniform distributions, $\divt{} \sim U(0, \divt{max})$.
    The estimated probability of the method inferring one divergence event, $p(\hat{\numt{}} = 1)$,
    is given for each \divt{max}.
    Each plot represents 500 simulation replicates analyzed using $5\e6$
    samples from the prior.
}{figPowerPsiMode}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_omega_prob.pdf}{
    The bias of the model-averaging approach of \citet{Hickerson2013} to
    support one divergence event in our simulation-based power analyses.
    The plots illustrate histograms of the estimated posterior probability that
    the dispersion index of divergence times is less than 0.01 ($p(\vmratio{} <
    0.01 | \ssSpace)$) from analyses of simulated datasets where \divt{} for 22
    pairs of populations is drawn from a series of uniform distributions,
    $\divt{} \sim U(0, \divt{max})$.
    The proportion of simulation replicates that strongly support one
    divergence event, $p(BF_{\vmratio{} < 0.01, \vmratio{} \geq 0.01} > 10)$,
    is given for each \divt{max}.
    Each plot represents 500 simulation replicates analyzed using $5\e6$
    samples from the prior.
}{figPowerOmegaProb}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_num_excluded.pdf}{
    The propensity of the model-averaging approach of \citet{Hickerson2013} to exclude
    the truth in our simulation-based power analyses.
    The plots illustrate the number of true \divt{} parameters excluded from analyses of
    simulated datasets where \divt{} for 22 pairs of populations is drawn from a series of
    uniform distributions, $\divt{} \sim U(0, \divt{max})$. The proportion
    of simulation replicates in which at least one true parameter value is excluded from
    the model preferred by a Bayes factor ($p(\divt{} \notin \hat{M})$) is
    given for each \divt{max}.
    Each plot represents 500 simulation replicates analyzed using $5\e6$
    samples from the prior.
}{figPowerNumExcluded}

\mFigure{../../model-choice/results/power-1/pymsbayes-results/plots/power_prob_exclusion.pdf}{
    The propensity of the model-averaging approach of \citet{Hickerson2013} to
    exclude the truth in our simulatoin-based power analyses.  The plots
    illustrate the estimated posterior probability of excluding at least one
    true \divt{} value from analyses of simulated datasets where \divt{} for 22
    pairs of populations is drawn from a series of uniform distributions,
    $\divt{} \sim U(0, \divt{max})$. The proportion of simulation replicates in
    which there is strong support for at least one true parameter value being
    excluded from the model ($p(BF_{\divt{} \notin M, \divt{} \in M} > 10)$) is
    given for each \divt{max}.
    Each plot represents 500 simulation replicates analyzed using $5\e6$
    samples from the prior.
}{figPowerProbExclusion}

%% Validation results
\mFigure{../../model-choice/results/validation/results/pymsbayes-results/plots/mc_behavior.pdf}{
    An assessment of the approximate Bayesian model-averageing approach of
    \citet{Hickerson2013} under the ideal conditions when the prior model
    is correct (i.e., the pseudo-replicate datasets are simulated from
    parameters drawn from the same prior distributions used in the
    analysis).
    The plots show the relationship between the estimated posterior and true
    probability of (A \& C) $\numt{}=1$ and (B \& D) $\vmratio{} < 0.01$, based
    on 50,000 simulations.
    The results summarize the (A \& B) unadjusted and (C \& D) GLM-adjusted
    posterior estimate from each simulation replicate.
    The prior settings for all replicates included five prior models with
    $\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
    U(0.0001, 0.05)$ for all five models, and
    $M_1: \divt{} \sim U(0, 0.1)$,
    $M_2: \divt{} \sim U(0, 1)$,
    $M_3: \divt{} \sim U(0, 5)$,
    $M_4: \divt{} \sim U(0, 10)$, and
    $M_5: \divt{} \sim U(0, 20)$.
    The number of samples from the prior was $2.5\e6$.
    The simulated data structure was 8 population pairs, with a single 1000
    bp locus sampled from 10 individuals from each population.  The 50,000
    estimates of the posterior probability of one divergence event were
    assigned to 20 bins of width 0.05.
    The estimated posterior probability of each bin is plotted against the
    proportion of replicates in that bin with a true value consistent with
    one divergence event (i.e., $\numt{}=1$ or $\vmratio{} < 0.01)$.
}{figValidationMCBehavior}

\mFigure{../../response-redux/results/sampling-error/pymsbayes-results/omega_over_sampling.pdf}{
    Traces of the estimated lower and upper limits of the 95\% highest posterior density (HPD)
    interval of \vmratio{} (the dispersion index of divergence times) as 100 million prior
    samples are accumulated. Each pair of points is based on 1000 posterior samples retained
    from the prior. Both (A) unadjusted and (b) GLM-regression-adjusted estimates are shown.
    Prior settings were $\divt{} \sim U(0,10)$, $\meanDescendantTheta{} \sim U(0.0005, 0.04)$,
    and $\ancestralTheta{} \sim U(0.0005, 0.02)$.
}{figSamplingError}

%% Model-choice tau prior
\mFigure{../../model-choice/tau-prior/tau_prior.pdf}{
    The prior distribution on divergence times imposed by the model-averaging prior
    comprised of five models with different uniform priors on \divt{}:
    $M_1$ ($\divt{} \sim U(0, 0.1)$), $M_2$ ($\divt{} \sim U(0, 1)$), $M_3$
    ($\divt{} \sim U(0, 5)$), $M_4$ ($\divt{} \sim U(0, 10)$), $M_5$ ($\divt{}
    \sim U(0, 20)$).
}{figMCTauPrior}

%:FIGURE-saturation plot
\mFigure{../../saturation/saturation-plot.pdf}{
    The summary statistics $\pi$ \citep{Tajima1983} and $\pi_{net}$
    \citep{Takahata1985} as a function of divergence time between populations.
    Each plot represents 1100 pairs of parameter draws and summary statistics
    calculated from the simulated data.
    Prior settings for the simulations were $\divt{} \sim U(0, 20)$,
    $\meanDescendantTheta{} \sim U(0.0005, 0.04)$, and $\ancestralTheta{} \sim
    U(0.0005, 0.02)$.
}{figSaturationPlot}

% \mFigure{../../response-redux/results/hickerson/pymsbayes-results/pymsbayes-output/d1/m12345678-combined/mean_by_dispersion.pdf}{
%     Results of reanalysis.
% }{figJointPosterior}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}

\singlespacing

\renewcommand{\refname}{\noindent\MakeUppercase{\LARGE\sffamily\upshape supporting information}}

% PUT MAIN TEXT CITATION HERE
% \begin{thebibliography}{1}
% \providecommand{\natexlab}[1]{#1}
% \providecommand{\url}[1]{\texttt{#1}}
% \providecommand{\urlprefix}{URL }

% \bibitem

% \end{thebibliography}

%% SUPPL TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{table}{0}

\end{document}

>>>>

Recently, this journal has served as a medium for a
discussion of the potential pitfalls of approximate Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the approximate Bayesian model choice method,
\msb, which estimates the temporal distribution of divergences among
co-distributed pairs of taxa \citep{Huang2011} by sampling over all
unordered models of divergence.
\citet{Oaks2012} published results of simulation-based power analyses
showing that \msb can often be biased toward inferring models of temporally
clustered divergence times across taxon pairs.
\citet{Hickerson2013} published a response to this paper where they present
an empirical Bayes model-averaging approach that they conclude circumvents the
poor behavior of the method revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
The main difference in perspectives are centered around
(1) the mechanism by which broad uniform priors cause the poor behavior of
\msb, and
(2) how to potentially mitigate this issue.

@@
